%				Description of thesis
%
%Name of candidate		Stuart Lee Wakefield
%Title of thesis			Distributed data analysis over the grid and a study of the decay MSSM 							A/H -> tau tau -> two jets at CMS.

%\vspace{5cm}

CMS is one of two general purpose detectors at the Large Hadron Collider at CERN. During each year of operation CMS will collect 10 petabytes of data, which must be reliably stored and made available for analysis by physicists around the world. CMS has adopted a computing model based on Grid technology. A prototype distributed analysis framework for CMS is presented. This framework enabled CMS physics analysis to be performed at distributed sites. An evaluation of this tool was performed by  members of the CMS Higgs analysis group. The results of this evaluation were used in the redesign of the CMS distributed analysis software.

$\tau$ leptons can be used as a tool in the identification of several physics processes. In 65\% of cases the $\tau$ decays hadronically to form a jet. The development of a Monte Carlo jet energy correction is presented along with a proposed method for obtaining the correction from real data using jet plus $\gamma$ events.

In the Minimally Superymmetric Standard Model (MSSM) heavy neutral Higgs boson decays copiously to 2 $\tau$ leptons. A study of $gg \rightarrow A/H \rightarrow 2 \tau$ jets using missing energy for event selection is presented. The expected $\tan\beta$ sensitivity of CMS with 60~\fb of data is presented and compared with previous studies which made use of b-tagging in the associated channel $gg \rightarrow bbH \rightarrow 2 \tau$ jets.
