\chapter{Acronyms}

\begin{description}

\item[ALICE] A Large Ion Collider Experiment.
\item[AliEn] Alice EnviroNment.
\item[AOD] Analysis Object Data.
\item[APD] Avalanche PhotoDiode.
\item[API] Application Programming Interface.
\item[ATLAS] A Toroidal LHC Apparatus. 
\item[BOSS] Batch Object Submission System.
\item[BR] Branching Ratio. 
\item[CMS CAF] CMS Cern Analysis Facility. 
\item[CE] Computing Element. 
\item[CLI] Command Line Interface.
\item[CMS] Compact Muon Solenoid.
\item[CPU] Central Processing Unit.
\item[CRAB] Cms Remote Analysis Builder.
\item[CSC] Cathode Strip Chambers. 
\item[DB] Database. 
\item[DBS] Dataset Bookeeping System.
\item[DIRAC] Distributed Infrastructure with Remote Agent Control.
\item[DLS] Data Location Service.
\item[DM] Data Management
\item[DOM] DOcumnet Model.
\item[DQM] Data Quality Monitoring.
\item[DT] Drift Tube.
\item[EB] Ecal Barrel.
\item[ECAL] Electromagnetic CALorimeter.
\item[EDG] European DataGrid. 
\item[EE] Electromagnetic calorimter Endcap.
\item[EGEE] Enabling Grids for E-sciencE.
\item[FTP] File Transfer Protocol. 
\item[GCT] Global Calorimeter Trigger.
\item[GROSS] GRidified Orca Submision System.
\item[GUID] Globally Unique IDentifier. 
\item[HB] Hadron calorimeter Barrel.
\item[HCAL] Hadron CALorimeter.
\item[HE] Hadron Endcap.
\item[HEPCAL] HEP common application layer for analysis
\item[HF] Hadron calorimeter Forward.
\item[HI] Heavy Ion.
\item[HLT] High Level Trigger.
\item[HO] Hadron calorimter Outer.
\item[HTML] HyperText Markup Language.
\item[II] Information Index.
\item[IO] Input Output.
\item[JDL] Job Description Language.
\item[JIM] Job and Information Monitoring
\item[LB] Logging and Bookeeping.
\item[LCG] Lhc Computing Grid.
\item[LFN] Logical File Name.
\item[LHC] Large Hadron Collider.
\item[LRC] Local Replica Catalog.
\item[MC] Monte Carlo. 
\item[MSSM] Minimal Supersymmetric Standard Model. 
\item[ORCA] Object-oriented Reconstruction for CMS Analysis.
\item[OSG] Open Science Grid.
\item[PFN] Physical File Name.
\item[PRS] Physics Reconstruction and Selection.
\item[RB] Resource Broker. 
\item[RLI] Replica Location Index.
\item[RLS] Replica Location Service.
\item[RMC] Replica Management Catalogue.
\item[RPC] REsistive Plate Chamber.
\item[SAM] Sequential Access via Metadata.
\item[SAX] Simple Api for Xml.
\item[SE] Storage Element.
\item[SM] Standard Model.
\item[SOAP] Simple Object Access Protocol.
\item[SPS] Super Proton Synchrotron.
\item[SQL] Structured Query Language.
\item[SRM] Storage Resource Manager.
\item[SUSY] SUperSYmmetry.
\item[SWIG] Simplified Wrapper and Interface Generator.
\item[TB] Test Beam. 
\item[TDR] Technical Design Report. 
\item[TEC] Tracker EndCap.
\item[TIB] Tracker Inner Barrel.
\item[TID] Tracker Inner Disk.
\item[TOB] TRacker Outer Barrel.
\item[UI] User Interface.
\item[VO] Virtual Organisation.
\item[WM] Workflow Management.
\item[WMS] Workload Management System.
\item[WN] Worker Node.
\item[XML] eXtensible Markup Language.
\item[XSL] Xml Stylesheet Language.

\end{description}
